Are we living in a depressive society?

### 2024-04-03 outputs/paper/paper.qmd
commit

>>>>

# Load necessary libraries
library(tidyverse)
library(lubridate)

# Define the path to the data file and load it
data <- read.csv(file = here::here("outputs/data/Overall_trends.csv"))

# Convert 'Time Period End Date' to date format and then extract year and month
data$`Time Period End Date` <- as.Date(data$`Time Period End Date`, format="%m/%d/%Y")
data$YearMonth <- format(data$`Time Period End Date`, "%Y-%m")

# Filter the dataset for the specified symptoms
filtered_data <- data %>%
  filter(Indicator %in% c('Symptoms of Depressive Disorder', 
                          'Symptoms of Anxiety Disorder', 
                          'Symptoms of Anxiety Disorder or Depressive Disorder'))

# Plotting the line graph
ggplot(filtered_data, aes(x = YearMonth, y = Value, group = Indicator, color = Indicator)) +
  geom_line() +
  labs(title = "Symptom Rates Over Time",
       x = "Date (Year and Month)",
       y = "Symptom Rates (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
